Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-11-18 paper/tex/appendix.tex
clarify chippr reference and move to footnote

``Stacking'' according to
\begin{equation}
  \label{eq:stacked}
  \hat{N}^{H}(z) \equiv \frac{1}{N_{tot}}\ \sum_{i}^{N_{tot}}\ \hat{p}^{H}_{i}(z)
\end{equation}
is the most widely accepted method for obtaining $\hat{N}^{H}(z)$ as an estimator of the redshift distribution from \pzpdf s derived by a method $H$.
Though the use of the stacked estimator of the redshift distribution is not formally correct \citep{Malz:chippr}, we use it under the untested assumption that the response of our metrics of $\hat{N}^{H}(z)$ will be analogous to the same metrics applied to a principled estimator of the redshift distribution.

>>>>

``Stacking'' according to
\begin{equation}
  \label{eq:stacked}
  \hat{N}^{H}(z) \equiv \frac{1}{N_{tot}}\ \sum_{i}^{N_{tot}}\ \hat{p}^{H}_{i}(z)
\end{equation}
 is the most widely used method for obtaining $\hat{N}^{H}(z)$ as an estimator of the redshift distribution from \pzpdf s derived by a method $H$. While the stacked estimator of the redshift distribution violates the mathematical definition of statistical independence and is thus not formally correct\footnote{\citet{Malz:chippr} shows how the stacking procedure can lead to bias in the estimate of $N(z)$ and presents a principled alternative to this commonly employed method.}, we use it as a basis for comparison of \pzpdf\ methods under the untested assumption that the response of our metrics of $\hat{N}^{H}(z)$ will be analogous to the same metrics applied to a principled estimator of the redshift distribution.

%is the most widely accepted method for obtaining $\hat{N}^{H}(z)$ as an estimator of the redshift distribution from \pzpdf s derived by a method $H$.  This procedure is not formally correct, basic statistics tells us that joint probabilities are not formed by adding probabilities.  \citet{Malz:chippr} shows how the stacking procedure can lead to bias in redshift estimates, and develop a principled alternative to this commonly employed method.  However, while  the use of the stacked estimator of the redshift distribution is not formally correct, we use it under the untested assumption that the response of our metrics of $\hat{N}^{H}(z)$ will be analogous to the same metrics applied to a principled estimator of the redshift distribution.
